Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging

### 2020-06-15 article.tex
Further revisions

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser-Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy (2PLM) showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. To date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm. Fifteen camera exposures ranging between 50 $\mu$s and 80 ms {Parthasarathy:2008el, Atchia:2013ep, Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages.

@@

Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}. Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event \cite{Kazmi:2015du}. This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}. This paper utilizes the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.

@@

Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical O2 vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.). Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific Corp.). Mice were placed supine in a stereotaxic frame (Kent Scientific Corp.) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure. The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates. A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion. A 3 mm round cover glass (\#1, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void. Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull. A layer of C\&B-Metabond (Parkell, Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure. A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements. The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging. They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear, belt-driven treadmill awake imaging system \cite{He:2020}.

@@

Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function. After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

@@

In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) was estimated using the 5 ms exposure speckle contrast frames. Cross-sectional profiles were extracted from each vessel at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution. Because LSCI is most sensitive to moving scatterers, i.e. erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel. The vascular flux was then computed by scaling MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}. Relative changes in vascular flux and perfusion were calculated using the average of the entire awake state as the baseline.

@@

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure1.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:system_image}
        (a) MESI system schematic with 2x magnification: L1 (f = 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 (f = 100 mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.). (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
    }
\end{figure}

>>>>

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) during photothrombotic stroke induction observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. To date, no study has directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

@@

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) synchronized with the modulated laser pulses with 2x magnification and cropped to a field-of-view of 3.6 x 3.0 mm. Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages \cite{Sullender:2018ff}.

@@

Because $\tau_c$ is inversely related to the speed of the moving scatterers \cite{Bonner:1981hg,Briers:1996kfa}, the inverse correlation time ($ICT = 1/\tau_c$) is frequently used as a metric for quantifying blood flow in vasculature and perfusion in parenchyma \cite{Ayata:2004ba,Strong:2005kj,Sullender:2018ff}. Recent work to improve the quantitative accuracy of MESI flow measurements in vasculature takes into account the presence of multiple dynamic scattering events instead of assuming only a single dynamic scattering event per photon \cite{Kazmi:2015du}. This is achieved by scaling the fitted $ICT$ value by the diameter of the vessel in order to obtain an estimate of "vascular flux” that better accounts for variations in vascular volume sampling \cite{Kazmi:2015du,Richards:2017df}. This paper utilizes the vascular flux metric (arbitrary units) for all vessel measurements and $ICT$ (s$^{-1}$) for all parenchymal perfusion measurements.

@@

Mice ($n = 4$, C57BL/6J, male, 4-6 months, Charles River Laboratories, Inc.) were anesthetized with medical $O_2$ vaporized isoflurane (3\% for induction, 1-2\% for maintenance, 0.5 L/min) via nose-cone inhalation. Body temperature was maintained at 37 $^\circ$C with a feedback heating pad (DC Temperature Controller, Future Health Concepts, Inc.). Arterial oxygen saturation, heart rate, and breathing rate were monitored via pulse oximetry (MouseSTAT, Kent Scientific Corp.). Mice were placed supine in a stereotaxic frame (Kent Scientific Corp.) and subcutaneously administered carprofen (5 mg/kg) and dexamethasone (2 mg/kg) to reduce inflammation during the craniotomy procedure. The scalp was shaved and resected to expose the skull between the bregma and lambda cranial coordinates. A 3 mm diameter portion of the skull over the somatosensory cortex was removed with a dental drill (Ideal Microdrill, 0.8 mm burr, Fine Science Tools, Inc.) while under regular artificial cerebrospinal fluid (buffered pH 7.4) perfusion. A 3 mm round cover glass (\#1, World Precision Instruments, Inc.) was placed over the exposed brain with artificial cerebrospinal fluid filling the void. Gentle pressure was applied to the cover glass while Kwik-sil adhesive (World Precision Instruments, Inc.) was deposited to bond the glass to the skull. A layer of C\&B-Metabond (Parkell, Inc.) was applied over the Kwik-sil to create a sterile, air-tight seal around the craniotomy and to allow for the restoration of intracranial pressure. A second layer of C\&B-Metabond was used to cement a custom titanium head-plate centered around the cranial window for head-constrained awake measurements. The subjects were allowed to recover from surgery and monitored for cranial window integrity and normal behavior for at least four weeks prior to imaging. They were then exposed to head fixation during 20-30 minute sessions over 3-5 days until habituated to locomotion on a linear, belt-driven treadmill awake imaging system \cite{He:2020}.

@@

Cranial window implanted mice ($n = 3$) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure proper function. After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

@@

In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) was estimated using the 5 ms exposure speckle contrast frames. Cross-sectional profiles were extracted from each vessel at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution. Because LSCI is most sensitive to moving scatterers, i.e. erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel. The vascular flux was then computed by scaling the MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}. Relative changes in vascular flux and perfusion were calculated using the average of the entire awake state as the baseline.

@@

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure1.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:system_image}
        (a) MESI system schematic with 2x magnification: L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685$\pm$20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.). (b) Single exposure (5 ms) LSCI and MESI inverse correlation time during awake and anesthetized states in the same subject (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
    }
\end{figure}

### 2020-06-15 cover_letter.tex
Further revisions

In this paper, we present cerebral blood flow measurements in awake mice during the induction of general anesthesia with isoflurane. We utilize multi-exposure speckle imaging (MESI) to highlight the large anatomical changes caused by the vasodilatory inhalant. We also characterize the impact of the anesthesia on cortical hemodynamics across multiple subjects and imaging sessions.

This work is significant because it provides a unique insight into the acute effects of general anesthesia. Existing studies have largely focused on before and after point measurements of cortical hemodynamics whereas we present wide-field imagery during the induction itself. These results provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.

>>>>

In this paper, we present cerebral blood flow measurements in awake mice during the induction of general anesthesia with isoflurane. We utilize multi-exposure speckle imaging (MESI) to highlight the large anatomical changes caused by the vasodilatory inhalant. We also characterize the impact of anesthesia on cortical hemodynamics across multiple subjects and imaging sessions.

This work is significant because it provides a unique insight into the acute effects of general anesthesia. Existing studies have largely focused on discrete measurements before and after the induction of anesthesia whereas we present wide-field imagery during the induction itself. These results provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
